More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex
comments on lemma 2

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\LUDO}[1]{\textcolor{green}{#1}}
\newcommand{\RAB}[1]{\textcolor{magenta}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

   \begin{small}\begin{proof}
Consider rule TR2 in 
       Definition~\ref{def:operationalSemantics}. 
	\begin{description}
		\item[{\bf Tr2:}]
	\end{description}
	\noindent
    $\inferrule
    {
	\forall m\!\!\in\!\! I_1. {\pNet_m \models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
\\     	
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',\beta_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{
    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip

@@

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\mprset{myfraction=\reddottedrule}\inferrule
		{
			\{{\beta_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\subst{\beta_{j_0}\leftarrow v_Q}\land\Pred\,',  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{small}

@@

       Consider each premise of the open transition (constructed by \textbf{Tr2} in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV_k=\SV{\alpha_j^{j\in I\uplus\{j_0\}\uplus 
	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
	are the 
    set of leaves and holes of $P$, $I_1\uplus I_2$ and $J'$ are the sets of moving 
    leaves and holes 
    in the reduction of $P$. All sub-pNets of 
    must
    be 
reduced, we need:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[
    	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
    	\models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \]\[
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\]
%\forall m\!\!\in\!\! I\cup \{j_0\}. 	
%    {\left(\begin{array}{l}
%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
%    	\{\xrightarrow{\beta_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
%		{ \pNet_m 
%    	 \models
%    	\inferrule*[myfraction=\reddottedrule]
%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
%    	{\ostate{s_m} \OTarrow {v_m}
%    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
%\end{array}\right)}\]
the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
by hypothesis, the other open transitions are immediate consequence of the open 
transition that can be performed by $P$ (premises of \textbf{Tr2}).
The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
and the ones for $Q$: 
$I'_{PQ}= I'_P \uplus I'_Q$, similarly the moving holes are the union of the moving 
holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)$. By definition 
$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)\Leftrightarrow
	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, \beta_j=\alpha_j \land 
	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
	$\Pred\,''=\Pred\subst{\beta_{j_0}\leftarrow 
	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}

>>>>

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\definecolor{darkgreen}{rgb}{0.1, 0.5, 0.1}
\newcommand{\LUDO}[1]{\textcolor{darkgreen}{#1}}
\newcommand{\RAB}[1]{\textcolor{magenta}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

   \begin{small}\begin{proof}
Consider rule TR2 in 
       Definition~\ref{def:operationalSemantics}.

\noindent\textbf{Tr2:}\\
	\noindent
\begin{mathpar}
    \mprset {vskip=1ex}
\inferrule
    {
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',\beta_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\mprset{myfraction=\reddottedrule}\inferrule
    		{
    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}

@@

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\mprset{myfraction=\reddottedrule}\inferrule
	{
		\{{\beta_j}\}^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\mprset{myfraction=\reddottedrule}\inferrule
		{
			\{{\beta_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\TODO{important comment added:}
Note that this does not mean that any two pNets can be composed and produce an open 
transition. Indeed, the predicate $\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q}$ might not 
be satisfiable if the open transition of $Q$ cannot be matched with $\beta_{j_0}$.

\LUDO{Question/comment: this formulation makes the proof easy and supposes that we use 
enough 
variables, which is in accordance with the implementation and the way we define SV, but I 
believe that $\Pred\,'\land \beta_{j_0}= v_Q$ might be better because more flexible and 
less dependant of the way OTs are defined}

\begin{small}

@@

       Consider each premise of the open transition (constructed by \textbf{Tr2} in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV_k=\SV{\alpha_j^{j\in I\uplus\{j_0\}\uplus 
	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
	are the 
    set of leaves and holes of $P$, $I_1\uplus I_2$ and $J'$ are the sets of moving 
    leaves and holes 
    in the reduction of $P$. All sub-pNets of 
    must
    be 
reduced, we need:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[
    	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
    	\models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \]\[
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\]
%\forall m\!\!\in\!\! I\cup \{j_0\}. 	
%    {\left(\begin{array}{l}
%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
%    	\{\xrightarrow{\beta_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
%		{ \pNet_m 
%    	 \models
%    	\inferrule*[myfraction=\reddottedrule]
%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
%    	{\ostate{s_m} \OTarrow {v_m}
%    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
%\end{array}\right)}\]
the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
by hypothesis, the other open transitions are immediate consequence of the open 
transition that can be performed by $P$ (premises of \textbf{Tr2}).
The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
and the ones for $Q$: 
$I'_{PQ}= I'_P \uplus I'_Q$, similarly the moving holes are the union of the moving 
holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)$. By 
definition 
$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)\Leftrightarrow
	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, \beta_j=\alpha_j \land 
	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
	$\Pred\,''=\Pred\subst{\beta_{j_0}\leftarrow 
	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}
